---
title: "Reproducible Research - assessment 1"
author: "V. Demydov"
date: "Saturday, February 14, 2015"
output: html_document
---

## 1. Mean steps number

```{r}
setwd("D:/stud/courcera/rep_r")
acTable<-read.csv('activity.csv')
stepsByDays<-tapply(acTable$steps,acTable$date,sum)
hist(stepsByDays)
ss<-summary(stepsByDays)
ss[4]
ss[3]
```
## 2. 5-min intervals
```{r}
stepsByInterval<-aggregate(steps~interval,data=acTable,mean)
plot(stepsByInterval$interval,stepsByInterval$steps,type='l')
maxInt<-stepsByInterval$interval[which.max(stepsByInterval$steps)]
```
Interval containing maximum number of steps is `r maxInt`

## 3. Imputing missing values
```{r}
naCalc<-length(acTable$steps[acTable$steps=='NA'])
```
Total number of missing values in the dataset is `r naCalc`
```{r}
meanByDays<-aggregate(steps~date,data=acTable,mean)
meanSteps<-mean(acTable$steps,na.rm=T)
fillTable<-acTable
fillTable$steps[is.na(fillTable$steps)]<-meanSteps
stepsByDays<-tapply(fillTable$steps,fillTable$date,sum)
hist(stepsByDays)
ss<-summary(stepsByDays)
ss[4]
ss[3]
```
I am sorry, I understood that my filling tactics is not very good (but I could select any). I tried to fill from aggregated table but could not find command like vlookup in Excel. All my construction caused error.

##4. Are there differences in activity patterns between weekdays and weekends?
```{r}
fillTable$nc<-weekdays(as.Date(fillTable$date)) %in% c("субота", "неділя")
stepsByIntervalWork<-aggregate(steps~interval,data=fillTable[fillTable$nc==FALSE,],mean)
stepsByIntervalWeekend<-aggregate(steps~interval,data=fillTable[fillTable$nc==TRUE,],mean)
par(mfrow=c(2,1))
par(mar=c(4,4,2,1))
plot(stepsByIntervalWeekend$interval,stepsByIntervalWeekend$steps,type='l',xlab='',ylab='Number of steps',main='weekend')
plot(stepsByIntervalWork$interval,stepsByIntervalWork$steps,type='l',xlab='interval',ylab='Number of steps',main='weekday')

```
